\documentclass[9pt, letterpaper]{article}

% Packages
\usepackage[left=0.4in, right=0.4in, top=0.3in, bottom=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{inputenc}
\usepackage{parskip}
\usepackage{microtype}
\renewcommand{\baselinestretch}{0.97}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    urlcolor=black,
    linkcolor=black
}

% No page numbers
\pagestyle{empty}

% Section formatting
\titleformat{\section}{\bfseries\large}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{2pt}

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \item[]
  \textbf{#1} \hfill \textbf{#2} \\
  \textit{#3} \hfill \textit{#4}
}

\setlist[itemize]{noitemsep, topsep=1pt, parsep=0pt, partopsep=0pt, leftmargin=1.2em}

\begin{document}

%----------HEADER----------
\begin{center}
    {\LARGE \textbf{SIMARAN SHAIKH}} \\[3pt]
    Ponda, Goa, India \quad|\quad
    +91 83299 39588 \quad|\quad
    \href{mailto:simaranshaikh04@gmail.com}{simaranshaikh04@gmail.com} \quad|\quad
    \href{https://www.linkedin.com/in/simaranshaikh}{linkedin.com/in/simaranshaikh}
\end{center}

%----------SUMMARY----------
\section{Professional Summary}
Results-driven B.Com (Financial Accounting) student with hands-on experience in financial data analysis (100+ companies), Power BI dashboard development, and equity research. Proficient in Advanced Excel, DAX, Power Query, and data visualization. Certified by Microsoft, AICTE, IBM, and NIELIT. Seeking entry-level roles in Finance Analytics, Business Intelligence, or MIS at a data-driven organization.

%----------SKILLS----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0em, label={}]
  \small{
    \item \textbf{Data \& BI Tools:} Microsoft Power BI (Desktop \& Service), Power Query, DAX, Data Modeling, Advanced Excel (VLOOKUP, Pivot Tables, Charts, IF/SUMIF), Google Sheets
    \item \textbf{Finance Skills:} Financial Ratio Analysis (65+ ratios), Equity Research, Portfolio Strategy, Financial Statement Analysis, Year-on-Year Trend Analysis, KPI Reporting
    \item \textbf{Analytics \& AI:} AI Analytics Tools, AI-Assisted Data Processing, Data Cleaning \& Transformation, Multi-Source Data Integration (Excel, CSV, Databases)
    \item \textbf{Other:} Data Visualization, Business Reporting, Cross-functional Collaboration, Project Coordination
  }
\end{itemize}

%----------EXPERIENCE----------
\section{Experience}

\begin{itemize}[leftmargin=0em, label={}]

  \resumeSubheading
    {UptoSkills – Finance Intern \& Team Captain (AICTE Internship Portal)}{February 2026 – Present}
    {Financial Parameter Analysis Project}{India (Remote)}
  \begin{itemize}
    \resumeItem{Led a cross-functional team through end-to-end data collection, analysis, and weekly reporting for the Financial Parameter Analysis project.}
    \resumeItem{Structured KPI data for \textbf{100+ companies} (FY2022–FY2024); computed \textbf{65+ financial ratios} (liquidity, profitability, leverage, efficiency) for 5+ companies across FY2020–FY2024.}
    \resumeItem{Conducted year-on-year analysis of revenue, profit/loss, and key ratios to surface growth trends and profitability shifts.}
    \resumeItem{\textbf{Tools:} Advanced Excel, AI Analytics Tools, Google Sheets}
  \end{itemize}

  \vspace{2pt}

  \resumeSubheading
    {FICE Education – Power BI Intern (Microsoft Elevate x AICTE Program)}{February 2026 – March 2026}
    {4-Week Emerging Technologies Internship}{India (Remote)}
  \begin{itemize}
    \resumeItem{Selected for the Microsoft Elevate x AICTE Internship (February 2026 Batch); completed Microsoft Learn courses on Power BI fundamentals and attended expert-led masterclasses on end-to-end BI workflows.}
    \resumeItem{Built a \textbf{UPI Transaction Analytics Dashboard} on a 250,000-row dataset featuring \textbf{9 custom DAX measures} across 3 report pages — covering transaction volume trends, fraud detection, and demographic segmentation.}
    \resumeItem{Developed additional dashboards: Loan Default Prediction (67,000-row Kaggle dataset), GST Compliance (Indian state-level data), and Bankruptcy Prediction (US public company data).}
    \resumeItem{Proficient in data cleaning (Power Query / M code), data modeling, table relationships, and multi-source data integration.}
    \resumeItem{Passed program assessment; earned \textbf{co-branded Microsoft \& AICTE certificate}.}
    \resumeItem{\textbf{Tools:} Power BI Desktop, Power BI Service, Power Query, DAX, Data Modeling}
  \end{itemize}

  \vspace{2pt}

  \resumeSubheading
    {Don Bosco College, Panjim – Student Coordinator \& Intern}{March 2026}
    {Certificate Course: Equity Research \& Portfolio Strategy}{Panaji, Goa}
  \begin{itemize}
    \resumeItem{Coordinated a 30-hour certificate course (40-seat B.Com cohort) in collaboration with IQAC; managed logistics, student communication, and scheduling across Saturday sessions.}
    \resumeItem{Completed internship case work at Precision Investments: designed a recovery equity portfolio for a client with \textbf{Rs. 5L investment intent \& Rs. 3L deployed at -14\%}; rebuilt a mutual fund portfolio targeting \textbf{Rs. 1.2L annual income}; built a \textbf{Rs. 50L equity portfolio from scratch}; conducted equity research on Dynamatic Technologies.}
  \end{itemize}

\end{itemize}

%----------EDUCATION----------
\section{Education}

\begin{itemize}[leftmargin=0em, label={}]
  \resumeSubheading
    {Don Bosco College, Panjim}{June 2024 – April 2027 (Expected)}
    {Bachelor of Commerce (B.Com) – Financial Accounting}{Goa, India}

  \vspace{1pt}

  \resumeSubheading
    {Deepvihar Higher Secondary School}{June 2022 – April 2024}
    {Higher Secondary School Certificate (HSSC) – Commerce}{}
\end{itemize}

%----------CERTIFICATIONS----------
\section{Certifications}
\begin{itemize}[leftmargin=0em, label={}]
\small{
\item \textbf{Business Intelligence Using Advanced Excel and Power BI} – Microsoft \& AICTE (2026) \quad|\quad \textbf{Advanced Excel with AI} – Internshala (2025)
\item \textbf{AI Literacy} – IBM (Credly) \& NIELIT \quad|\quad \textbf{Equity Research \& Portfolio Strategy} – Don Bosco College / IQAC (2026)
\item \textbf{Business Management Training Programme} – Digital Marketing, Brand Management \& Promotion \quad|\quad \textbf{Internship \& Job Preparation} – Internshala (2026)
}
\end{itemize}

%----------PROJECTS----------
\section{Key Projects}

\begin{itemize}
  \resumeItem{\textbf{UPI Transaction Analytics Dashboard (Power BI):} 250,000-row dataset; 9 DAX measures; 3-page report covering transaction trends, fraud patterns, and demographic segmentation.}
  \resumeItem{\textbf{Loan Default Prediction Dashboard (Power BI):} 67,000-row Kaggle dataset; Power Query data cleaning; risk segmentation visuals for banking use case.}
  \resumeItem{\textbf{GST Compliance Dashboard (Power BI):} State-level India GST data; compliance gap analysis and regional KPI tracking.}
  \resumeItem{\textbf{Financial Parameter Analysis (Excel):} KPIs for 100+ companies; 65+ ratios across FY2020–FY2024 for financial benchmarking.}
\end{itemize}

\end{document}
