%-------------------------
% ATS-Friendly Resume - Simaran Shaikh
%-------------------------
\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{geometry}

\geometry{top=0.35in, bottom=0.35in, left=0.5in, right=0.5in}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%---------- HEADING ----------
\begin{center}
    {\Huge \scshape Simaran Shaikh} \\ \vspace{4pt}
    \small Ponda, Goa, India \quad $|$ \quad
    \href{tel:8329939588}{8329939588} \quad $|$ \quad
    \href{mailto:simaranshaikh04@gmail.com}{simaranshaikh04@gmail.com} \quad $|$ \quad
    \href{https://www.linkedin.com/in/simaranshaikh}{linkedin.com/in/simaranshaikh}
\end{center}

%---------- PROFESSIONAL SUMMARY ----------
\section{Professional Summary}
\small{
Detail-oriented B.Com (Financial Accounting) undergraduate with hands-on experience analyzing financial data for 100+ companies, computing 65+ financial ratios, and building interactive Power BI dashboards. Certified in Advanced Excel (Internshala), Power BI (Microsoft \& AICTE), and AI Literacy (IBM--Credly, TCS iON). Adept at leveraging AI-assisted tools and data analytics to drive actionable business insights. Seeking entry-level roles in Finance, Data Analytics, or MIS at a data-driven organization.
}

%---------- EXPERIENCE ----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Finance Intern \& Team Captain}{February 2026 -- Present}
    {UptoSkills (AICTE Internship Portal)}{India}
    \resumeItemListStart
      \resumeItem{Selected through AICTE's national internship initiative; led a cross-functional team ensuring timely delivery of data collection, analysis, and reporting tasks.}
      \resumeItem{Executed the Financial Parameter Analysis project, collecting and structuring KPI data for 100+ companies across FY2022--FY2024.}
      \resumeItem{Computed 65+ financial ratios (liquidity, profitability, leverage, efficiency) for 5+ companies across FY2020--FY2024 to evaluate financial performance and trends.}
      \resumeItem{Conducted year-on-year analysis of revenue, profit/loss, and key ratios to identify growth trends and profitability shifts.}
      \resumeItem{Utilized Advanced Excel and AI-assisted analytics tools to enhance data accuracy and analytical efficiency; consistently met weekly reporting targets.}
      \resumeItem{\textbf{Tools:} Advanced Excel, AI Analytics Tools, Financial Modeling, KPI Dashboards}
    \resumeItemListEnd

  \resumeSubheading
    {Power BI Intern -- Microsoft Elevate Program}{February 2026 -- Present}
    {Edunet Foundation (Microsoft \& AICTE)}{India}
    \resumeItemListStart
      \resumeItem{Selected for the Microsoft Elevate x AICTE 4-Week Internship on Emerging Technologies (February 2026 Batch), focusing on Power BI and data visualization.}
      \resumeItem{Built end-to-end proficiency in data cleaning and transformation using Power Query, data modeling, table relationships, and multi-source data integration (Excel, CSV, databases).}
      \resumeItem{Developed interactive dashboards and visual reports in Power BI Desktop using DAX formulas; published and shared reports via Power BI Service.}
      \resumeItem{Solved a real-world business problem under industry mentor guidance; passed program assessment and earned a co-branded Microsoft \& AICTE certificate.}
      \resumeItem{\textbf{Tools:} Power BI Desktop, Power BI Service, Power Query, DAX, Data Modeling, Data Visualization}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%---------- SKILLS ----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Data \& Analytics:} Advanced Excel (VLOOKUP, Pivot Tables, Macros), Power BI Desktop \& Service, Power Query, DAX, Financial Ratio Analysis, KPI Dashboards, Data Cleaning \& Transformation \\
    \textbf{Finance:} Financial Statement Analysis, Year-on-Year Trend Analysis, Profitability \& Liquidity Ratios, Revenue Modeling, MIS Reporting \\
    \textbf{AI \& Emerging Tech:} AI-Assisted Analytics, Generative AI, AI Literacy (IBM--Credly, TCS iON) \\
    \textbf{Tools \& Platforms:} Microsoft Excel, Power BI, CSV/Database Integration, AICTE Internship Portal
  }}
\end{itemize}

%---------- EDUCATION ----------
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {Don Bosco College, Panjim}{June 2024 -- April 2027}
    {Bachelor of Commerce (B.Com) -- Financial Accounting}{Goa, India}

  \resumeSubheading
    {Deepvihar Higher Secondary School}{June 2022 -- April 2024}
    {Higher Secondary School Certificate (HSSC) -- Commerce}{Goa, India}

\resumeSubHeadingListEnd

%---------- CERTIFICATIONS ----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Advanced Excel with AI} -- Internshala \quad $|$ \quad
    \textbf{Business Intelligence Using Advanced Excel \& Power BI} -- AICTE \\
    \textbf{AI Literacy} -- IBM (Credly) \& TCS iON \quad $|$ \quad
    \textbf{Getting Started with Generative AI} \quad $|$ \quad
    \textbf{Digital Marketing \& Brand Management} -- Business Management Training Programme \\
    \textbf{Internship \& Job Preparation} -- Internshala (December 2025 -- January 2026)
  }}
\end{itemize}

%---------- KEY ACHIEVEMENTS ----------
\section{Key Achievements}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    $\bullet$ Analyzed financial data for \textbf{100+ companies} across 3 fiscal years as part of a structured AICTE internship project. \\
    $\bullet$ Computed \textbf{65+ financial ratios} across 5+ companies spanning a 5-year period (FY2020--FY2024). \\
    $\bullet$ Appointed \textbf{Team Captain} among intern cohort, overseeing cross-functional collaboration and timely deliverables. \\
    $\bullet$ Earned co-branded \textbf{Microsoft \& AICTE} certification by successfully completing a real-world BI project under mentor guidance.
  }}
\end{itemize}

\end{document}
